%======================================================================================================
% ============================================ References =============================================
%======================================================================================================


\begin{thebibliography}{}
\justifying

%======================== Theory ===============================	
\bibitem{bib:whitbeck-2013}
WHITBECK, A. J. \textit{Discovery and characterization of a Higgs-like resonance using the matrix element likelihood approach}. Thesis (Doctor of Philosophy) - Johns Hopkins University, Baltimore, 162 p., 2013. Available at: http://inspirehep.net/record/1286374/files/. Accessed on: 19 aug. 2017.

\bibitem{bib:brachem-2012}
BRACHEM, C. \textit{Studies for a top quark mass measurement using the matrix element method in the semileptonic channel}. Dissertation (Master of Particle Physics) - Georg-August-Universität, Göttingen, 94 p., 2012. Available at: http://physik2.uni-goettingen.de/research/high-energy/publications/MastersBrachem.pdf. Accessed on: 21 aug. 2017.

\bibitem{bib:griffiths-2008}
GRIFFITHS, D. \textit{Introduction to elemtary particles}. New York: Wiley, 2008.

\bibitem{bib:halzen-martin-1984}
HALZEN, F.; MARTIN, A. D. \textit{Quarks and leptons: an introductory course in modern particles physics}. New York: Wiley, 1984.

\bibitem{bib:PhysRevD-86-1-2012}
BERINGER, J. \textit{et al.} (Particle Data Group). Review of Particle Physics, \textit{Physics Review D}, USA, v. 86, n. 1, p. 1528, 2012.

\bibitem{bib:quigg-1983}
QUIGG, C. \textit{Gauge theories of the strong, weak and electromagnetic interactions}. New York: Westview Press, 1983.

\bibitem{bib:PhysLettB-126-1983}
ARNISON, G. \textit{et al.} Experimental observation of lepton pairs of invariant mass around 95-GeV/$c^2$ at the CERN SPS collider. \textit{Physics Letters B}, USA, v. 126, n. 18, p.398, 1983.

\bibitem{bib:EurophysNews-14-10-1983}
BRIANTI, G.; GABATHULER, E. Intermediate vector bosons. Production and identification at the CERN proton anti-proton collider. \textit{Europhysics News}, France, v. 14, n. 10, p. 1, 1983.

\bibitem{bib:JPhys-447-1-2013}
VARELA, J. Measurement of the properties of the 125 GeV Higgs boson with the CMS detector. \textit{Journal of Physics}, USA, v. 447, n. 1, p. 012010, 2013.

\bibitem{bib:das-2008}
DAS, A. \textit{Lectures on quantum field theory}. Singapore: World Scientific, 2008.

\bibitem{bib:seiden-2008}
SEIDEN, A. \textit{Particle physics: a comprehensive introduction}. San Francisco: Addison Wesley, 2005.

\bibitem{bib:ellis-2003}
ELLIS, R. K.; STIRLING W. J.; WEBBER, B. R. \textit{QCD and collider physics}. Cambridge: Cambridge University Press, 2003.

\bibitem{bib:PhysRev22-579-1961}
GLASHOW, S. L. Partial symmetries of weak interactions. \textit{Nuclear Physics}, v. 22, p. 579, 1961.

\bibitem{bib:PhysRevLett19-1264-1967}
WEINBERG, S. A model of leptons. \textit{Physics Review Letters}, v. 19, p. 1264, 1967.

\bibitem{bib:CMS-PAS-HIG-14-038}
CMS COLLABORATION. Search for invisible decays of Higgs bosons in the vector boson fusion production mode. \textit{CMS-PAS-HIG-14-038}. CERN, 2014.

\bibitem{bib:ATLAS-CONF-2015-004}
ATLAS COLLABORATION. Search for an invisibly decaying Higgs boson produced via vector boson fusion in pp collisions at $\sqrt{s}$=8TeV using ATLAS detector at the LHC. \textit{ATLAS-CONF-2015-004}. CERN, 2015.

\bibitem{bib:JPhys-455-1-2013}
FILIPPIS, N. Search for the Standard Model Higgs in $H~\rightarrow~ZZ~\rightarrow~4l$ channel with the CMS experiment. \textit{Journal of Physics}, USA, v. 455, n. 1, p. 012027, 2013.

\bibitem{bib:CMS-HIG-13-002}
CMS COLLABORATION. Properties of the Higgs-like boson in the decay $H~\rightarrow~ZZ~\rightarrow~4l$ in pp collisions at $\sqrt{s}=7$ e 8 TeV. \textit{CMS Physics Analysis Summary}, n. 002, CERN, 2013.

\bibitem{bib:PhysRevLett110-081803-2013}
CMS COLLABORATION. Study of the mass and spin-parity of the Higgs boson candidate via its decays to Z boson pairs. \textit{Physics Review Letters}, v. 110,	p. 081803, 2013.

\bibitem{bib:PhysRevD89-092007-2014}
CMS COLLABORATION. Measurement of the properties of a Higgs boson in the four-lepton	final state. \textit{Physics Review D}, USA, v. 89, p. 092007, 2014.

\bibitem{bib:LHC-Higgs-XSWG-2018}
LHC HIGGS CROSS SECTION WORKING GROUP. Available at: https://twiki.cern.ch/twiki/bin/view/LHCPhysics/CERNYellowReportPageAt1314TeV2014$\#$s$\_$13$\_$0$\_$TeV. Accessed on: 29/11/2018.

\bibitem{bib:IFAE-14-2008}
BOZZI, G. \textit{et al.} Vector boson pair production via vector boson fusion at NLO QCD. \textit{XVI Incontri di Fisica delle Alte Energie}, Italy, v. 14, p. 69, 2008.

\bibitem{bib:PhysRevD98-030001-2018}
Tanabashi, M \textit{et al.} (Particle Data Group) Review of Particle Physics. \textit{Physics Review D}, USA, v. 98, n. 9, p. 030001, 2018.

\bibitem{bib:Dittmaier_et_al_2011}
DITTMAIER, S. ~\textit{et al.} \textit{Handbook of LHC Higgs cross sections}: 1 inclusive observables. Switzerland: CERN, LHC, 2011, 153 p.

\bibitem{bib:Dittmaier_et_al_2012}
DITTMAIER, S. ~\textit{et al.} \textit{Handbook of LHC Higgs cross sections}: 2 differential distributions. Switzerland: CERN, LHC, 2012, 257 p.

\bibitem{bib:Dittmaier_et_al_2013}
DITTMAIER, S. ~\textit{et al.} \textit{Handbook of LHC Higgs cross sections}: 3 Higgs properties. Switzerland: CERN, LHC, 2013, 404 p.

\bibitem{bib:PhysRev88-051801-2002}
PLEHN, T.; RAINWATER, D. L.; ZEPPENFELD, D. Determining the structure of Higgs couplings at the CERN large hadron collider. \textit{Physics Review Letters}, USA, v. 88, p. 051801, 2002.

\bibitem{bib:PhysLettB136-3-1984}
CAHN, R. N.; DAWSON, S. Production of very massive Higgs bosons. \textit{Physics Letters B}, USA, v. 136, n. 3, p. 196, 1984.

\bibitem{bib:PhysRep457-1-2005}
DIJOUDI, A. The anatomy of electro-weak symmetry breaking. Tome I: the Higgs boson in the Standard Model. \textit{Physics Reports}, USA, v. 457, n. 1, p. 1, 2005.

\bibitem{bib:NuclPhysB287-1987}
ALTARELLI, G.; MELE, B.; PITOLLI, F. Heavy Higgs bosons production at future colliders. \textit{Nuclear Physics B}, USA, v. 287, n. 1, p. 205, 1987.

\bibitem{bib:Phys46-203-1998}
SPIRA, M. QCD effects in Higgs physics. \textit{Fortsch Physics}, USA, v. 46, p. 203, 1998.

\bibitem{bib:PhysRevLett69-3274-1992}
HAN, T.; VALENCIA, G.; WILLENCROCK, S. Structure-function approach to vector-boson scattering in pp collisions. \textit{Physics Review Letters}, USA, v. 69, p. 3274, 1992.

\bibitem{bib:PhysRevD77-053010-2008}
HARLANDER, R. V.; VOLLINGA, J.; WEBER, M. M. Gluon-induced weak boson fusion. \textit{Physics Review D}, USA, v. 77, p. 053010, 2008.

\bibitem{bib:PhysRevLett105-011801-2010}
BOLZONI, P. \textit{et al.} Higgs boson production via vector-boson fusion at next-to-next-to-leading order in QCD. \textit{Physics Review Letters}, USA, v. 105, p. 011801, 2010.

\bibitem{bib:ChinPhysC-38-9-2014}
OLIVE, K. A. \textit{et al.} (Particle Data Group). Review of Particle Physics. \textit{Chinese Physics Courier}, China, v. 38, n. 9, p. 1676, 2014.

\bibitem{bib:PhysRevD62_013009_2000}
ZEPPENFELD, D. \textit{et al.} Measuring Higgs boson couplings at the LHC. \textit{Physics Review D}, USA, v. 62, p. 013009, 2000.

\bibitem{bib:PhysLettB-736-64-2014}
CMS COLLABORATION. Constraints on the Higgs boson width from off-shell production and decay to Z-boson pairs. \textit{Physics Letters B}, USA, v. 736, p. 64, 2014.

\bibitem{bib:PhysRevD92-012004-2015}
CMS COLLABORATION. Constraints on the spin-parity and anomalous HVV couplings of the Higgs boson in proton collisions at 7 and 8 TeV. \textit{Physics Review D}, USA, v. 92, p. 012004, 2015.

\bibitem{bib:PhysRevD92-072010-2015}
CMS COLLABORATION. Limits on the Higgs boson lifetime and width from its decay to four charged leptons. \textit{Physics Review D}, USA, v. 92, p. 072010, 2015.

\bibitem{bib:CMS-AN-16-442}
CMS COLLABORATION. Measurements of properties of the Higgs boson in the four-lepton final state at $\sqrt{s}=$ 13TeV. \textit{CMS Analysis Notes}, CERN, n. 442, 2016.

\bibitem{bib:CMS-AN-16-328}
CMS COLLABORATION. Search for dark matter produced in association with a Higgs boson in the four lepton final state at 13 TeV. \textit{CMS Analysis Notes}, CERN, n. 328, 2016.

%\bibitem{bib:langacker-2009}
%LANGACKER, P.
%\newblock{The Standard Model and Beyond},
%\newblock{New York: CRC Press}, 2009.

%\bibitem{bib:PhysRevLett13-321-1964}
%ENGLERT, F. and BROUT, R.
%\newblock{Broken Symmetry and the Mass of Gauge Vector Mesons}.
%\newblock{Physics Review Letters}, v. 13, p. 321, 1964.

%======================== LHC and CMS =================================
\bibitem{bib:web-cern}
CERN WEB SITE. Available at: http://home.web.cern.ch/about. Accessed on: 24 nov. 2017.

\bibitem{bib:lhc-guide}
CERN. \textit{LHC The Guide}. CERN-Brochure-2008-001-Eng. Available at: http://cds.cern.ch/record/1092437/files/CERN-Brochure-2008-001-Eng.pdf. Accessed on: 24 nov. 2017.

\bibitem{bib:Nature-448-2017}
BRUNING, O; COLLIER, P. Building a behemoth. \textit{Nature}, USA, v. 448, p. 258, 2007.

\bibitem{bib:JINST-3-362-2008}
CMS COLLABORATION. The CMS experiment at the CERN LHC. \textit{Journal of Instrumentation}, Italy, v. 3, p. 362, 2008.

\bibitem{bib:cms-page}
CMS WEB SITE. Available at: http://cms.web.cern.ch/. Accessed on: 20 nov. 2017.

\bibitem{bib:atlas-page}
ATLAS WEB SITE. Available at: http://atlas.ch/. Accessed on: 20 nov. 2017.

\bibitem{bib:atlas-page}
LHCB WEB SITE. Available at: http://lhcb.web.cern.ch/lhcb/. Accessed on: 20 nov. 2017.

\bibitem{bib:lhcf-page}
LHCF WEB SITE. Available at: http://home.web.cern.ch/about/experiments/lhcf. Accessed on: 20 nov. 2017.

\bibitem{bib:totem-page}
TOTEM WEB SITE. Available at: http://totem.web.cern.ch/Totem/. Accessed on: 20 nov. 2017.

\bibitem{bib:hcal-tdr-1997}
CMS COLLABORATION. CMS Technical Design Report: Hadron Calorimeter Technical Design Report. Available at: http://cds.cern.ch/record/357153/files/HCAL$\_$TDR1997.pdf?version=1. Accessed on: 20 nov. 2017.

\bibitem{bib:CMS-PTDR-2006}
CMS COLLABORATION. CMS Physics: Technical Design Report 1. Available at: http://cds.cern.ch/record/922757/files/lhcc-2006-001.pdf. Accessed on: 20 nov. 2017.

\bibitem{bib:grupen-2008}
GRUPEN, C.; SHWARTZ, B. \textit{Particle Detectors}. New York: Cambridge University Press, 2008.

\bibitem{bib:CMS-MSTDR-1997}
CMS COLLABORATION. \textit{CMS Technical Design Report: The Muon Project}. Available at: http://cds.cern.ch/record/343814/files/LHC-97-032.pdf. Accessed on: 20 nov. 2017. 

\bibitem{bib:CMS-DAS-TDR-2002}
CMS COLLABORATION. \textit{CMS The TriDAS Project Technical Design Report 2: Data Acquisition and High-Level Trigger}. Available at: https://cdsweb.cern.ch/record/578006/files/cer-2336481.pdf. Accessed on: 20 nov. 2017.

\bibitem{bib:Pigard-2017}
PIGARD, P. \textit{Electron studies and search for vector boson scattering in events with four leptons and two jets with the CMS detector at the LHC}. Thesis (Doctor of Philosophy) - Universite Paris-Saclay, France, 181 p., 2017. Available at: https://cds.cern.ch/record/2290139. Accessed on 19 aug. 2018.


%================== Analysis ==============================		
\bibitem{bib:JHEP_07_2008_060}
ALIOLI, S. ~\textit{et al.} NLO vector-boson production matched with showed in POWHEG. \textit{Journal of High Energy Physics}, Italy, v. 07, p. 060, 2008.
	
\bibitem{bib:JHEP_11_2004_040}
NASON, P. A new method for combining NLO QCD with shower Monte Carlo algorithms. \textit{Journal of High Energy Physics}, Italy, v. 11, p. 040, 2004.

\bibitem{bib:JHEP_11_2007_070}
FRIXIONE, S.; NASON, P.; OLEARI, C. Matching NLO QCD computations with parton shower simulations: the POWHEG method. \textit{Journal of High Energy Physics}, Italy, v. 11, p. 070, 2007.

\bibitem{bib:JHEP_02_2012_088}
BAGNASHI, E. ~\textit{et al.} Higgs production via gluon fusion in the POWHEG approach in the SM and in the MSSM. \textit{Journal of High Energy Physics}, Italy, v. 02, p. 088, 2012.

\bibitem{bib:JHEP_02_2010_037}
NASON, P.; OLEARI, C. NLO Higgs boson production via vector-boson fusion matched with shower in POWHEG. \textit{Journal of High Energy Physics}, Italy, v. 02, p. 037, 2010.

\bibitem{bib:PhysRev_D91_2015_9_094003}
HARTANTO, H. B. ~\textit{et al.} Higgs boson production in association with top quarks in the POWHEG BOX. \textit{Physics Review D}, USA, v. 91, p. 094003, 2015.

\bibitem{bib:JHEP_10_2013_083}
LUISONI, G. ~\textit{et al.} $HW^{\pm}/HZ$ + 0 and 1 jet at NLO with the POWHEG BOX interfaced to GoSam and their merging within MiNLO. \textit{Journal of High Energy Physics}, Italy, v. 10, p. 083, 2013.

\bibitem{bib:PhysRev_D81_2010_075022}
GAO, Y. ~\textit{et al.} Spin determination of single-produced resonances at hadron colliders. \textit{Physics Review D}, USA, v. 81, p. 075022, 2010.

\bibitem{bib:JHEP_04_2015_040}
NNPDF COLLABORATION. Parton distributions for the LHC Run II. \textit{Journal of High Energy Physics}, Italy, v. 04, p. 040, 2015.

\bibitem{bib:EurPhysJ_C74_2014_1_2702}
NASON, P.; ZANDERIGHI, G. $W^{+}W^{-}$, $WZ$, $ZZ$ production in the POWHEG-BOX-V2. \textit{European Physics Journal C}, France, v. 74, p. 2702, 2014.

\bibitem{bib:NuclPhysProcSuppl_205_2010_10}
CAMPBELL, J. M.; ELLIS, R. K. MCFM for the Tevatron and the LHC. \textit{Nuclear Physics Proceedings Supplements}, v. 205, p. 10, 2010.

\bibitem{bib:JHEP_04_2014_060}
CAMPBELL, J. M.; ELLIS, R. K.; WILLIAMS, C. Bounding the Higgs width at the LHC using full analytic results for $gg \rightarrow e^{-}e^{+}\mu^{-}\mu^{+}$. \textit{Journal of High Energy Physics}, v. 04, p. 060, 2014.

\bibitem{bib:NuclInstrumMeth_A506_2003_250}
GEANT4 COLLABORATION. GEANT4 a simulation toolkit. \textit{Nuclear Instruments and Methods A}, v. 506, p. 250, 2003.

\bibitem{bib:IEEETransNuclSci_53_2006_270}
GEANT4 COLLABORATION. GEANT4 developments and applications. \textit{IEEE Transactions on Nuclear Science}, v. 53, p. 270, 2006.

\bibitem{bib:CMS-AN-16-359}
CMS COLLABORATION. Measurement of the total and differential ZZ production cross sections, $Z \rightarrow ll l'l'$ branching fraction and a TGCs in pp collisions at $\sqrt{s} = $13 TeV. \textit{CMS Analysis Notes}, n. 359, CERN, 2016.

\bibitem{bib:CMS-AN-16-217}
CMS COLLABORATION. New results on the study of Higgs boson production in the four-lepton final state at $\sqrt{s}=$ 13TeV. \textit{CMS Analysis Notes}, n. 217, CERN, 2016.

\bibitem{bib:JINST-10-2015-P06005}
CMS COLLABORATION. Performance of electron reconstruction and selection with the CMS detector in proton-proton collisions at $\sqrt{s}=$ 8 TeV. \textit{Journal of Instrumentation}, v. 10, p. 06005, 2015.

\bibitem{bib:CMS-AN-15-215}
CMS COLLABORATION. Measurement of the muon-tracking efficiency using the tag and probe method on 2015 RunII data. \textit{CMS Analysis Notes}, n. 215, CERN, 2015.

\bibitem{bib:CMS-AN-15-277}
CMS COLLABORATION. Measurement of the properties of the Higgs boson in the four-lepton final state at $\sqrt{s}=$ 13 TeV. \textit{CMS Analysis Notes}, n. 277, CERN, 2016.

\bibitem{bib:JHEP11_047_2017}
CMS COLLABORATION. Measurements of properties of the Higgs boson decaying into the four-lepton final state in pp collisions at $\sqrt{s}=$ 13TeV. \textit{Journal of High Energy Physics}, v. 11, p. 047, 2017.

\bibitem{bib:SimonHaykin}
HAYKIN, S. \textit{Neural Networks and Learning Machines}. New York: Pearson, 2009.

\bibitem{bib:KevinGurney}
GURNEY, K. \textit{An Introduction to Neural Networks}. New York: UCL Press, 2004.

\bibitem{bib:GlorotAndBendio2010}
GLOROT, X.; BENGIO, Y. Understanding  the  difficulty  of training deep feedforward neural networks. \textit{International Conference  on  Artificial Intelligence  and  Statistics}, p. 249, 2010.

\bibitem{bib:NairAndHinton2010}
NAIR, V.; HINTON, G. E. Rectified  linear  units  improve restricted  boltzmann machines. \textit{International Conference on Machine Learning}, p. 807, 2010.

\bibitem{bib:Zeiler_et_al2013}
ZEILER, M. D. ~\textit{et al.} On rectified linear units for speech processing. \textit{IEEE International Conference on Acoustics, Speech and Signal Processing}, p. 235, 2013.

\bibitem{bib:nnintro}
JORDAN, J. \textit{Neural networks: representation}. Available at: https://www.jeremyjordan.me/intro-to-neural-networks/. Accessed on: 28 mai. 2018.

\bibitem{bib:glouppe-ESWB-2018-1}
LOUPPE, G. Machine Learning: Lecture 1. \textit{Electroweak Symmetry Break Spring School} (EWSB), Italy.
2018. Available at: https://indico.cern.ch/event/673580/contributions/2790019/. Accessed on: 05 nov. 2018.

\bibitem{bib:undergoodoverfit1}
SCIKIT-LEARN WEB PAGE. \newblock{Underfit vs. Overfit}. Available at: https://scikit-learn.org/stable/auto$\_$examples/model$\_$selection/plot$\_$underfitting$\_$overfitting.html. Accessed on: 28 mai. 2018.

\bibitem{bib:undergoodoverfit2}
JORDAN, J. \textit{Deep neural networks: preventing overfitting}. Available at: https://www.jeremyjordan.me/deep-neural-networks-preventing-overfitting/. Accessed on: 28 mai. 2018.

\bibitem{bib:KerasWebPage}
KERAS WEB PAGE. Available at: https://keras.io/. Accessed on: 12 jan. 2016.

\bibitem{bib:JPhysConfSer_898_072046_2017}
BAGOLY, A. ~\textit{et al.} Machine learning developments in ROOT. \textit{Journal of Physics Conference Series}, v. 898, p. 072046. 2017.

\bibitem{bib:NPPS-10-205}
CAMPBELL, J. M.; ELLIS, R. K. MCFM for the Tevatron and the LHC. \textit{Nuclear Physics Proceeding Supplements}, v. 10, p. 205, 2010.

\bibitem{bib:PhysRevD-88-2013-034032}
BONVINI, M. ~\textit{et al.} Signal-background interference effects in $gg \rightarrow H \rightarrow WW$ beyond leading order. \textit{Physical Review D}, USA, v. 88, p. 034032, 2013.

\bibitem{bib:PhysLettB-774-2015-43}
MELNIKOV, K.; DOWLING, M. Production of two Z-bosons in gluon fusion in the heavy top quark approximation. \textit{Physical Letters B}, v. 744, p. 43, 2015.

\bibitem{bib:JHEP-1508-2015-065}
LI, C. S. ~\textit{et al.} Soft gluon resummation in the signal-background interference process of gg($\rightarrow$ h∗) $\rightarrow$ ZZ. \textit{Journal of High Energy Physics}, v. 1508, p. 065, 2015.

\bibitem{bib:PhysRevLett-98-2007-222002}
CATANI, S.; GRAZZINI, M. An NNLO subtraction formalism in hadron collisions and its application to Higgs boson production at the LHC. \textit{Physics Review Letters}, v. 98, p. 222002, 2007.

\bibitem{bib:JHEP-02-2008-043}
GRAZZINI, M. NNLO predictions for the Higgs boson signal in the H $\rightarrow$ WW $\rightarrow$ lnu lnu and H $\rightarrow$ ZZ $\rightarrow$ 4l decay channels. \textit{Journal of High Energy Physics}, v. 02, p. 043, 2008.

\bibitem{bib:JHEP-09-2013-129}
GRAZZINI, M.; SARGSYAN, H. Heavy-quark mass effects in Higgs boson production at the LHC. \textit{Journal of High Energy Physics}, v. 09, p. 129, 2013.

\bibitem{bib:CMS-AN-12-367}
CMS COLLABORATION. Updated results on the new boson discovered in the search for the standard model Higgs boson in the $H \rightarrow ZZ \rightarrow 4l$ channel in pp collisions at $\sqrt{s}=$ 7 and 8 TeV. \textit{CMS Analysis Notes}, n. 367, CERN, 2012.

\bibitem{bib:CMS-AN-13-108}
CMS COLLABORATION. Measurement of the production and decay of a Higgs boson in the four-lepton final state. \textit{CMS Analysis Notes}, n. 108, CERN, 2013.

\bibitem{bib:CMS-AN-12-141}
CMS COLLABORATION. Search for the standard model Higgs boson in the decay channel $H \rightarrow ZZ \rightarrow 4l$ in pp collisions. \textit{CMS Analysis Note}, n. 141, CERN, 2012.

\bibitem{bib:CMS-PAS-HIG-16-022}
CMS COLLABORATION. Search for associated production of Higgs bosons and top quarks in multilepton final states at $\sqrt{s}$ = 13 TeV. \textit{CMS Physics Analysis Summary}, n. 022, CERN, 2016.

\bibitem{bib:ATLAS-CONF-2017-041}
ATLAS COLLABORATION. Evidence for the $H \rightarrow b\bar{b}$ decay with the ATLAS detector. \textit{ATLAS Conference Notes}, n. 041, CERN, 2017.

\bibitem{bib:HiggsCombineToolWebPage}
\textit{Higgs Combine Tool Web Page}. Switzerland: CERN, 2012. Available at: https://legacy.gitbook.com/@cms-hcomb. Accessed on: 08 jun. 2016.

\bibitem{bib:PoS-ACAT2010-057}
MONETA, L. ~\textit{et al.} The RooStats Project. \textit{Proceeding of Science}, v. ACAT2010, p. 057, 2010.

\bibitem{bib:HiggsCombineToolFNALWorkshop2018}
\textit{HIGGS COMBINE TOOL WORKSHOP}. Batavia: Fermilab (FNAL), 2018. Available at: https://indico.cern.ch/event/747340/timetable/. Accessed on: 27 nov. 2018.

\bibitem{bib:MIT-650}
\textit{Wilk’s theorem}; A Likelihood Ratio Test for Nested Composite Hypothesis. Massachusetts: Massachusetts Institute of Technology (MIT), 2018. Available at: https://math.mit.edu/~rmd/650/wilks.pdf. Accessed on: 01 nov. 2018.

\bibitem{bib:UCBerkeley-26-2018}
BARTLETT, P. \textit{Theoretical Statistics}: Lecture 26. California: University of California, 2018. Available at: https://www.stat.berkeley.edu/~bartlett/courses/2013spring-stat210b/notes/26notes.pdf. Accessed on: 01 nov. 2018.

\bibitem{bib:GlenCowan}
COWAN, G.. \textit{Statistical Data Analysis}. Oxford: Clarendon Press, 1998.

\bibitem{bib:Eilam-ESWB-2018-1}
GROSS, E. ~\textit{et al.} Search and discovery statistics in HEP: lecture 1. \textit{Electroweak symmetry break spring school} (EWSB), Italy, 2018. Available at: https://indico.cern.ch/event/673580/contributions/2790011/attachments/1638839/2615856/Statistics$\_$CERN$\_$2018$\_$part1.pdf. Accessed on: 05 nov. 2018.

\bibitem{bib:Eilam-ESWB-2018-2}
GROSS, E. ~\textit{et al.} Search and discovery statistics in HEP: lecture 2. \textit{Electroweak symmetry break spring school} (EWSB), Italy, 2018. Available at: https://indico.cern.ch/event/673580/contributions/2790011/attachments/1638839/2615856/Statistics$\_$CERN$\_$2018$\_$part1.pdf. Accessed on: 05 nov. 2018.


%=================== CMS L1TT FNAL ===============================
\bibitem{bib:vertex-2017}
HAHN, K. ~\textit{et al.} \textit{L1 track finding for the CMS HL-LHC upgrade}. Switzerland: CERN, 2017. Available at: https://indico.cern.ch/event/627245/contributions/2677000/attachments/1524022/2382144/VERTEX2017-CMS-L1Tk-KristianHahn.pdf. Accessed on: 01 nov. 2018.

\bibitem{bib:cmsl1tt_fnal_package}
FNAL-FSU-TAMU CMSL1TT WORKING GROUPS. \textit{SLHCL1TrackTriggerSimulations}. Batavia: Fermilab (FNAL), 2016. Available at: https://github.com/jiafulow/SLHCL1TrackTriggerSimulations/wiki. Accessed on: 27 nov. 2017.

\bibitem{bib:CMS-TDR-17-001}
CMS COLLABORATION. The phase-2 upgrade of the CMS tracker. \textit{CMS Technical Design Report}, Switzerland: CERN, 2017.

\bibitem{bib:CMS-DN-15-025}
BAULIEU, G. ~\textit{et al.} Emulation of a track reconstruction system based on associative memories. \textit{Detector Notes}, Switzerland: CERN, 2015.

\bibitem{bib:fpga_xilinx}
XILINIX COMPANY. \textit{Field programmable gate array (FPGA)}. Available at: https://www.xilinx.com/products/silicon-devices/fpga/what-is-an-fpga.html. Accessed on: 27 jan. 2017.

\bibitem{bib:miqueias-cmsl1tt-19-01-16}
ALMEIDA, M. M.; JINDARIANI, S.; RISTORI, L. Synthetic efficiency study. \textit{Technical Simulation Report}, Batavia: Fermilab (FNAL), 2016. Available at: indico.cern.ch/event/485680/contributions/2004800/. Accessed on: 01 nov. 2018.

\bibitem{bib:miqueias-cmsl1tt-14-04-16}
ALMEIDA, M. M.; JINDARIANI, S.; RISTORI, L. Performance of simple duplicate removal strategy. \textit{Technical Simulation Report}, Batavia: Fermilab (FNAL), 2016. Available at: indico.cern.ch/event/520985/contributions/2136443/. Accessed on: 01 nov. 2018.
	
\bibitem{bib:miqueias-cmsl1tt-19-04-16}
ALMEIDA, M. M.; JINDARIANI, S.; RISTORI, L. Update on synthetic efficiency study. \textit{Technical Simulation Report}, Batavia: Fermilab (FNAL), 2016. Available at: indico.cern.ch/event/522593/contributions/2140692/. Accessed on: 01 nov. 2018.

\bibitem{bib:miqueias-cmsl1tt-27-04-17}
ALMEIDA, M. M.; JINDARIANI, S.; RISTORI, L. Synthetic Efficiency and Duplicate Removal. \textit{Technical Simulation Report}, Batavia: Fermilab (FNAL), 2017. Available at: indico.cern.ch/event/524621/contributions/2148537/. Accessed on: 01 nov. 2018.
	
\bibitem{bib:miqueias-cmsl1tt-17-08-17}
ALMEIDA, M. M.; JINDARIANI, S.; RISTORI, L. Using Bend Information in the AM - Performance Studies. \textit{Technical Simulation Report}, Batavia: Fermilab (FNAL), 2017. Available at: indico.cern.ch/event/660323/contributions/2693623/. Accessed on: 01 nov. 2018.
	
\bibitem{bib:pos-sissa-245-2016-057}
SZNAJDER, A.; ALMEIDA, M. M. A Fast Matrix Element Method (FastME). \textit{XXVII International Symposium on Lepton Photon Interactions at High Energies}, Ljubljana: SISSA, 2015. Available at: https://pos.sissa.it/245/057/pdf. Accessed on: 10 aug. 2016.

\bibitem{bib:tmva_manual}
HOECKER, A.  \textit{et. al.} \textit{TMVA4 toolkit for multivariate data analysis with ROOT (users guide)}, Switzerland: CERN, 2017. Available at: http://tmva.sourceforge.net/docu/TMVAUsersGuide.pdf. Accessed on: 30 mar. 2017.


%=============== FastME ==================================
\bibitem{bib:fastme_package}
ALMEIDA, M. M.; SZNAJDER, A. \textit{Fast Matrix Element Package} (FastME). Rio de Janeiro, 2016. Available at: https://github.com/mmelodea/FastMatrixElement. Accessed on: 27 nov. 2017.

\bibitem{bib:cms_mela}
BELUFFI, C. \textit{The matrix element method within CMS}. Switzerland: CMS, 2014. Available at: https://indico.cern.ch/event/258092/contributions/1588574/attachments/454217/629628/ACAT14.pdf. Accessed on: 27 nov. 2017.

\end{thebibliography}
