\begin{thebibliography}{}

%==== SM e Higgs =====
\bibitem{bib:Whitbeck}
WHITBECK, A. J.
\newblock{\em Discovery and Characterization of a Higgs-like Resonance using the Matrix Element Likelihood Approach}.
\newblock 2013. 162~p. Tese (Doctor of Philosophy) - Johns Hopkins University, Baltimore. Disponível em: $<$http://inspirehep.net/record/1286374/files/$>$. Acesso em: 19 ago. 2014.

\bibitem{bib:Brachem}
BRACHEM, C.
\newblock{\em Studies for a top quark mass measurement using the matrix element method in the semileptonic channel}.
\newblock 2012. 94~p. Dissertação (Master of Particle Physics) - Georg-August-Universität, Göttingen. Disponível em: $<$http://physik2.uni-goettingen.de/research/high-energy/publications/MastersBrachem.pdf.$>$. Acesso em: 21 ago. 2014.

\bibitem{bib:Chol}
CHOL, S.K. \textit{et al.}
\newblock Observation of a Resonance like Structure in the $\pi^{+-}\psi'$ Mass Distribution in Exclusive $B~\rightarrow~K\pi^{+-}\psi'$ Decays.
\newblock{\em Phys. Rev. Lett.}, USA, v. 100, n.14, p. 142001, Apr. 2008.

\bibitem{bib:Aalj}
AALJ, R. \textit{et al.}
\newblock Observation of the Resonant Character of the Z(4430) - State.
\newblock{\em Phys. Rev. Lett.}, USA, v. 112, n. 22, p. 222002, June 2014.

\bibitem{bib:Beringer}
BERINGER, J. \textit{et al.} (Particle Data Group)
\newblock{\em Phys. Rev. D}, USA, v. 86, n. 1, 1528 p., July 2012.

\bibitem{bib:Griffiths}
GRIFFITHS, D.
\newblock{\em Introduction to Elementary Particles}.
\newblock Weinheim: Wiley-VCH. 2ed. 2008.

\bibitem{bib:Halzen}
HALZEN, F.; MARTIN, A.D.
\newblock{\em Quarks and Leptons: an Introductory Course in Modern Particles Physics}.
\newblock New York: J. Wiley, 1984.

\bibitem{bib:Quigg}
QUIGG, C.
\newblock{\em Gauge Theories of the Strong, Weak and Electromagnetic Interactions}.
\newblock Menlo Park: Westview Press, 1983.

\bibitem{bib:Arnison}
ARNISON, G. \textit{et al.}
\newblock Experimental Observation of Lepton Pairs of Invariant Mass Around 95-GeV/$c^2$ at the CERN SPS Collider.
\newblock{\em Phys. Lett. B}, USA, v. 126, p. 398-410, July 1983.

\bibitem{bib:Brianti}
BRIANTI, G.; GABATHULER, E.
\newblock Intermediate vector bosons. Production and identification at the CERN proton anti-proton collider.
\newblock{\em Europhys. News}, France, v. 14, n. 10, p. 1-5, Nov. 1983.

\bibitem{bib:Varela}
VARELA, J.
\newblock Measurement of the properties of the 125 GeV Higgs boson with the CMS detector.
\newblock{\em J. Phys.}, USA, v. 447, n. 1, 012010, July 2013.

\bibitem{bib:Olive}
OLIVE, K.A. \textit{et al.} (Particle Data Group)
\newblock{\em Chin. Phys. C}, China, v. 38, n. 9, 1676 p., Sep. 2014.

\bibitem{bib:Filippis}
FILIPPIS, N.
\newblock Search for the Standard Model Higgs in $H~\rightarrow~ZZ~\rightarrow~4l$ channel with the CMS experiment.
\newblock{\em J. Phys.}, USA, v. 455, n. 1, 012027, Aug. 2013.

\bibitem{bib:HIG-13-002}
CMS COLLABORATION.
\newblock Properties of the Higgs-like boson in the decay $H~\rightarrow~ZZ~\rightarrow~4l$ in pp colisions at $\sqrt{s}=7$ e 8 TeV.
\newblock{\em CMS PAS HIG-13-002} (2013). Disponível em: $<$http://inspirehep.net/record/1230239?ln=pt$>$. Acesso em: 07 abr. 2014.

\bibitem{bib:Ashok} 
DAS, A.
\newblock{\em Lectures on Quantum Field Theory}.
\newblock Singapore: World Scientific, 2008.

\bibitem{bib:Seiden}
SEIDEN, A.
\newblock{\em Particle Physics: A Comprehensive Introduction}.
\newblock San Francisco: Addison Wesley, 2005.

\bibitem{bib:Ellis}
ELLIS, R.K.; STIRLING W.J.; WEBBER, B.R.
\newblock{\em QCD and Collider Physics}.
\newblock Cambridge: Cambridge University Press, 2003.

\bibitem{bib:Bozzi}
BOZZI, G. \textit{et al.}
\newblock Vector Boson Pair Production via Vector Boson Fusion at NLO QCD.
\newblock{\em IFAE 2007}, Italy, v. 14, p. 69-73, Apr. 2008.

\bibitem{bib:Langacker}
LANGACKER, P.
\newblock{\em The Standard Model and Beyond}.
\newblock New York: CRC Press, 2009.

%=== LHC =====
\bibitem{bib:web_cern}
CERN.
\newblock Disponível em: $<$http://home.web.cern.ch/about$>$. Acesso em: 24 nov. 2014.

\bibitem{bib:LHC_guide}
LHC GUIDE.
\newblock{\em CERN-Brochure-2008-001-Eng} (2008), 60 p.
\newblock Disponível em: $<$http://cds.cern.ch/record/1092437/files/CERN-Brochure-2008-001-Eng.pdf$>$. Acesso em: 24 nov. 2014.

\bibitem{bib:lhc_nature}
BRUNING, O; COLLIER, P.
\newblock Building a behemoth.
\newblock{\em Nature}, UK, v. 448, p. 285-289, July 2007.

\bibitem{bib:CMS_paper}
CMS Collaboration.
\newblock The CMS experiment at the CERN LHC.
\newblock{\em JINST}, Italy, v. 3, 362 p., Aug. 2008.

\bibitem{bib:CMS}
CMS.
\newblock Disponível em: $<$http://cms.web.cern.ch/$>$. Acesso em: 20 nov. 2014.

\bibitem{bib:ALICE}
ALICE.
\newblock Disponível em: $<$http://aliceinfo.cern.ch/Public/$>$. Acesso em: 25 nov. 2014.

\bibitem{bib:ATLAS}
ATLAS.
\newblock Disponível em: $<$http://atlas.ch/$>$. Acesso em: 25 nov. 2014.

\bibitem{bib:LHCb}
LHCb.
\newblock Disponível em: $<$http://lhcb.web.cern.ch/lhcb/$>$. Acesso em: 25 nov. 2014.

\bibitem{bib:LHCf}
LHCf.
\newblock Disponível em: $<$http://home.web.cern.ch/about/experiments/lhcf$>$. Acesso em: 25 nov. 2014.

\bibitem{bib:TOTEM}
TOTEM.
\newblock Disponível em: $<$http://totem.web.cern.ch/Totem/$>$. Acesso em: 25 nov. 2014.

\bibitem{bib:HCAL_TDR1997}
CMS Collaboration.
\newblock{\em CMS Technical Design Report: Hadron Calorimeter Technical Design Report}, 1997.
\newblock Disponível em: $<$http://cds.cern.ch/record/357153/files\\/HCAL$\_$TDR1997.pdf?version=1$>$. Acesso em: 27 nov. 2014.

\bibitem{bib:CMS_paper2006}
CMS Collaboration.
\newblock{\em CMS Physics: Technical Design Report 1}, 2006.
\newblock Disponível em: $<$http://cds.cern.ch/record/922757/files/lhcc-2006-001.pdf$>$Acesso em: 27 nov. 2014.

\bibitem{bib:Grupen}
GRUPEN, C.; SHWARTZ, B.
\newblock{\em Particle Detectors}.
\newblock New York: Cambridge University Press. 2ed. 2008.

%\bibitem{lhc_cs_cds}
%LHC Cross Section Layout.
%\newblock Disponível em: $<$http://cds.cern.ch/record/841539/\\files/lhc-pho-1998-341.jpg?version=1$>$. Acesso em: 27 nov. 2014.

\bibitem{bib:MS_TDR1997}
CMS Collaboration.
\newblock{\em CMS Technical Design Report: The Muon Project}, 1997.
\newblock Disponível em: $<$http://cds.cern.ch/record/343814/files/LHC-97-032.pdf$>$. Acesso em: 27 nov. 2014.

\bibitem{bib:DAQ}
CMS Collaboration.
\newblock{\em CMS The TriDAS Project Technical Design Report 2: Data Acquisition and High-Level Trigger}, 2002.
\newblock Disponível em: $<$https://cdsweb.cern.ch/\\record/578006/files/cer-2336481.pdf$>$. Acesso em: 01 dez. 2014.

%===== Higgs Width Analysis ======
\bibitem{Spira}
SPIRA, M. \textit{et al.}
\newblock Higgs Boson Production at the LHC.
\newblock{\em Nucl. Phys. B}, Netherlands, v. 453, p. 17-82, Oct. 1995.

\bibitem{HIG-14-002}
CMS COLLABORATION.
\newblock Constraints on the Higgs boson width from off-shell production and decay to $ZZ$ boson pairs. 
\newblock{\em CMS-PAS-HIG-14-002} (2014). Disponível em: $<$http://cds.cern.ch/record/1670066/?ln=pt$>$. Acesso em: 12 mai. 2014.

\bibitem{Covarelli}
COVARELLI, R.
\newblock{\em CERN Communication}. Disponível em: $<$http://home.web.cern .ch/about/updates/2014/03/cms-presents-new-boundary-higgs-width$>$. Acesso em: 19 set. 2014.

\bibitem{Melnikov}
MELNIKOV, K.; CAOLA, F.
\newblock Constraining the higgs boson width with $ZZ$ production at the LHC. Disponível em: $<$http://arxiv.org/abs/1307.4935$>$. Acesso em: 13 Jun. 2014.

\bibitem{Gunion}
GUNION, J.F.; HABER, H.E.; WUDKA, J.
\newblock Sum rules for Higgs bosons.
\newblock{\em Phys. Rev. D}, USA, v. 43, 3 ed., p. 904-912, Feb. 1991.

\bibitem{Dobrescu}
DOBRESCU, B.A.; LYKKEN, J.D.
\newblock Coupling spans of the Higgs-like boson.
\newblock{\em J. High Energy Phys.}, Italy, v. 2013, n. 2, Feb. 2013.

\bibitem{ATLAS-CONF-2013-011}
ATLAS COLLABORATION.
\newblock Search for invisible decays of a Higgs boson produced in association with a Z boson in ATLAS.
\newblock{\em ATLAS-CONF-2013-011}. Disponível em: $<$http://cds.cern.ch/record/1523696?ln=pt$>$. Acesso em: 27 jul. 2014.

\bibitem{Passarino}
KAUER, N.; PASSARINO, G.
\newblock Inadequacy of zero-width approximation for a light Higgs boson signal.
\newblock{\em J. High Energy Phys.}, Italy, v. 2012, n. 8, Aug. 2012.

%\bibitem{Kauer}
%KAUER, N.
%\newblock Inadequacy of zero-width approximation for a light Higgs boson signal.
%\newblock{\em Mod. Phys. Lett. A}, v. 28, 1330015, 2013.

\bibitem{AN-14-018}
AMAPHENE, N. \textit{et al.}
\newblock A measurement of the Higgs boson width using off-shell production and decay to 4 leptons.
\newblock{\em CMS AN-14-018} (2014). Disponível em: $<$http://inspirehep.net/record/$>$. Acesso em: 7 Dez. 2014.

\bibitem{Chatrchyan}
CHATRCHYAN, S. \textit{et al.}
\newblock Measurement of the properties of a Higgs boson in the four-lepton final state.
\newblock{\em Phys. Rev. D}, USA, v. 89, n. 9, p. 092007, May 2014.

\bibitem{Bolognesi}
BOLOGNESI, S. \textit{et al.}
\newblock Spin and parity of a single-produced resonance at the LHC.
\newblock{\em Phys.Rev. D}, USA, v. 86, n. 9, p. 095031, Nov. 2012.

\bibitem{Gao}
GAO, Y. \textit{et al.}
\newblock Spin determination of single-produced resonances at hadron colliders.
\newblock{\em Phys. Rev. D}, USA, v. 81, n. 7, p. 079905, Apr. 2010.

\bibitem{Handbook}
\newblock LHC Higgs Cross Section Working Group, S. Heinemeier, C. Mariotti, G. Passarino, R. Tanaka (Eds.), Handbook of LHC Higgs Cross Sections: 3. Higgs Properties, CERN-2013-004 (CERN, Geneva, 2013), DOI: 10.5170/CERN-2013-004.

\bibitem{Bredenstein}
BREDENSTEIN, A. \textit{et al.}
\newblock Precise predictions for the Higgs-boson decay $H~\rightarrow~WW/ZZ~\rightarrow~4$ leptons.
\newblock{\em Phys. Rev. D}, USA, v. 74, n. 1, p. 013004, July 2006.

\bibitem{Z4l}
CMS COLLABORATION.
\newblock Observation of Z decays to four leptons with the CMS detector at the LHC.
\newblock{\em CMS-SMP-12-009}. Disponível em: $<$http://arxiv.org/pdf/1210. 3844v2.pdf$>$. Acesso em: 10 dez. 2014.

\bibitem{Giacomo}
ORTONA, Giacomo.
\newblock Comunicação direta por e-mail em 3 dez. 2014.

\bibitem{Higgs_pack}
COMBINED LIMIT.
\newblock{\em Higgs Package}.
\newblock Disponível em: $<$https://github.com/HZZ4l$>$. Acesso em: 12 jun. 2014.

\end{thebibliography}